---
title: "DATA607 Week 3"
author: "ODONNELL"
date: "February 13, 2019"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(stringr)
```
```{r}
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
```

```{r}
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))

name
```

```{r}
phone <- unlist(str_extract_all(raw.data, "\\(?(\\d{3})?\\)?(-| )?\\d{3}(-| )?\\d{4}"))

phone
```

```{r}
#problem 3.1

#first_last <- unlist(str_extract_all(name, "[[:alpha:]]{2,}.+[[:alpha:]]{2,}"))

first_last <- unlist(str_extract_all(name, "[[:alpha:]]{2,}[[:space:]][[:alpha:]]{2,}"))

#"[[:alpha:]]{2,}(?!\\.)"

first_last
```
```{r}
#problem 3.2

unlist(str_detect(name, "[[:alpha:]]{2,}\\."))
```
```{r}
#problem 3.3

unlist(str_detect(name, "[[:alpha:]]{3,}[[:space:]][[:alpha:]]{3,}"))
```

4.1

[0-9]+\\$

  This captures the expression that ends in the
  most numbers 0-9. For example,
  "michael91"
  
4.2

\\b[a-z]{1,4}\\b

  This captures words that start with 1-4
  lowercase letters and ends with 1-4
  lowercase letters.
  For examples, "patagonia"
  
4.3

.*?\\.txt$

  This captures any string that ends in
  ".txt" which is great for identifying
  text files out of a list.
  For example, "michael.txt"
  
4.4 

\\d{2}/\\d{2}/\\d{4}

  This captures a string that has
  2 digits, then a forward slash,
  then 2 digits, then a forward slash,
  then 4 digits. For example,
  35/26/2543
  This would be great for
  identifying a date.
  
4.5

<(.+?)>.+?</\\1>

  This captures a string that starts with
  a group of characters that end with a period.
  Then, there's a second group of characters.
  For example,
  "M. ODonnell"